---
title: "Hotel Booking Prediction Model"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
author: Nimay Srinivasn
---

<!-- More information in R Markdown can be found at:
1. https://www.ssc.wisc.edu/sscc/pubs/RFR/RFR_RMarkdown.html  This is 
   the place to start since it is a short tutorial.
2. https://rmarkdown.rstudio.com/index.html This contains a longer 
   tutorial.  Take a look at the cheatsheet in 
   https://rmarkdown.rstudio.com/lesson-15.html, it is a concise 
   reference of R Markdown on two pages.
<-->

## Use this as a template for your homeworks.
#### Rename it to firstname-lastname.Rmd.
#### Run all the chunks by clicking on "Run" at the top right of the edit 
#### window and choose "Run All".  Assuming there were no errors in the
#### chunk, you should see a "Preview" button become visible on the top
#### left of the edit window.  Click this button and a html document should
#### pop up with the output from this R markdown script.

### Part 2.1-A
```{r}
library(plyr)
hotel = read.csv("/Users/sreevatsa/Downloads/hotel_bookings.csv", header = TRUE)
count(hotel, 'hotel') 
```
### Part 2.1-B.
```{r}
count(hotel, 'is_canceled') 
#Number of guests who canceled reservation: 44224
#Number of guests who did not cancel the reservation: 75166
```
### Part 2.1-C.
```{r}
count(hotel, 'customer_type')
# Customer type with the most reservations is Transient, with 89613 reservations
```

### Part 2.1-D.
```{r}
count(hotel, 'required_car_parking_spaces')
#7383 customers required the least number of parking spaces (1).
```

### Part 2.1-E.
```{r}
count(hotel, 'required_car_parking_spaces')
# 2 customers required the least number of parking spaces (8).
```

### Part 2.1-F.
```{r}
count(hotel, 'reserved_room_type')
count(hotel, 'assigned_room_type')
tt <- table(hotel$reserved_room_type == hotel$assigned_room_type)
round(100*prop.table(tt),digits = 2)
# 87.51% of the people who expressed a room preference during reservation got the room during check-in.
```
### Part 2.1-G.
```{r}
cancellation = (hotel['is_canceled'] == 'No') & (hotel['hotel'] == 'City Hotel')
travel = hotel[cancellation, 'country']
#travel.value_counts().head(10).plot(kind='barh',title='City Hotel')

cancellation = (hotel['is_canceled'] == 'No') & (hotel['hotel'] == 'Resort Hotel')
travel = hotel[cancellation, 'country']
#travel.value_counts().head(10).plot(kind='barh',title='Resort Hotel')
```
### Part 2.1-H.
```{r}

```

### Part 2.2.
```{r}
set.seed(1122)
index <- sample(1:nrow(hotel), 0.90*dim(hotel) [1])
train.df <- hotel[index,]
test.df <- hotel[-index, ]
dtree_train <- train.df[c('hotel','is_canceled','lead_time','adults','children','babies','meal','market_segment','distribution_channel',
'is_repeated_guest', 'previous_cancellations','previous_bookings_not_canceled','reserved_room_type','deposit_type','days_in_waiting_list',
'customer_type','adr','required_car_parking_spaces')]

dtree_test <- test.df[c('hotel','is_canceled','lead_time','adults','children','babies','meal','market_segment','distribution_channel',
'is_repeated_guest', 'previous_cancellations','previous_bookings_not_canceled','reserved_room_type','deposit_type','days_in_waiting_list',
'customer_type','adr','required_car_parking_spaces')]
```

### Part 2.2-A.
```{r}
library(rpart)
library(rpart.plot)
library(caret)
model <- rpart(is_canceled ~ ., method="class", data=dtree_train)
pred <- predict(model, dtree_train, type="class")
levels(pred)
table(pred)
confusionMatrix(pred,as.factor(dtree_train$is_canceled))
### Part 2.2-A.-i
rpart.plot(model, extra=104, fallen.leaves=T, type=4, main="tt")
### Part 2.2-A.-ii
# The list of important variables from the model and the output descion tree are 
#Deposit type (No Deposit, Refundabale and Non Refund)
#Lead time
#Previous Cancellations
### Part 2.2-A.-iii
model <- rpart(is_canceled ~ ., method="class", data=dtree_test)
pred <- predict(model, dtree_test, type="class")
confusionMatrix(pred,as.factor(dtree_test$is_canceled))
### Part 2.2-A.-iv
library(ROCR)
library("caret")
pred.rocr <- predict(model, newdata=dtree_test, type="prob")[,2]
f.pred <- prediction(pred.rocr, dtree_test$is_canceled)
f.perf <- performance(f.pred, "tpr", "fpr")
plot(f.perf, colorize=T, lwd=3)
abline(0,1)
auc <- performance(f.pred, measure = "auc")
cat(paste("The area under curve (AUC) for this model is ", round(auc@y.values[[1]], 3)))
```

### Part 2.3-A
```{r}
library(rpart)
library(rpart.plot)
library(caret)
model <- rpart(is_canceled ~ ., method="class", data=dtree_train, cp=0.0)
pred <- predict(model, dtree_train, type="class")
levels(pred)
table(pred)
confusionMatrix(pred,as.factor(dtree_train$is_canceled))
```
### Part 2.3-B
```{r}
```






